GeneSet_Expansion

### 2020-05-12 code/GeneSet_Expansion.Rmd
ReDo GeneSet enrichment

for( name in names(Expand_gt2)){
  eval(parse(text=paste0('set <- Expand_gt2$', 'name' )))
  ego <- enrichGO(gene            = set,
                    universe      = GENEsyb[,'hgnc_symbol'],
                    OrgDb         = org.Hs.eg.db,
                    keyType      = 'SYMBOL',
                    ont           = "ALL",
                    pAdjustMethod = "BH",
                    pvalueCutoff  = 0.01,
                    qvalueCutoff  = 0.05
                  )

@@

for( name in names(Expand_gt1)){
  eval(parse(text=paste0('set <- Expand_gt1$', 'name' )))
  ego <- enrichGO(gene            = set,
                    universe      = GENEsyb[,'hgnc_symbol'],
                    OrgDb         = org.Hs.eg.db,
                    keyType      = 'SYMBOL',
                    ont           = "ALL",
                    pAdjustMethod = "BH",
                    pvalueCutoff  = 0.01,
                    qvalueCutoff  = 0.05
                  )

>>>>

for( name in names(Expand_gt2)){
  eval(parse(text=paste0('set <- Expand_gt2$', name )))
  ego <- enrichGO(gene            = set,
                    universe      = GENEsyb[,'hgnc_symbol'],
                    OrgDb         = org.Hs.eg.db,
                    keyType      = 'SYMBOL',
                    ont           = "ALL",
                    pAdjustMethod = "BH",
                    pvalueCutoff  = 0.01,
                    qvalueCutoff  = 0.05
                  )

@@

for( name in names(Expand_gt1)){
  eval(parse(text=paste0('set <- Expand_gt1$', name )))
  ego <- enrichGO(gene            = set,
                    universe      = GENEsyb[,'hgnc_symbol'],
                    OrgDb         = org.Hs.eg.db,
                    keyType      = 'SYMBOL',
                    ont           = "ALL",
                    pAdjustMethod = "BH",
                    pvalueCutoff  = 0.01,
                    qvalueCutoff  = 0.05
                  )
